Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-16 mpaper/paper.tex
One more step towards completing the proof

\begin{abstract}
\end{abstract}

@@

\begin{lemma}[Perturbation Lemma
  \cite{layton2014numerical}] \label{prop:condition_number}
  Let $\lVert \cdot \rVert$ be any matrix norm, and let $\mathbf{A}$ and
  $\mathbf{E}$ be matrices such that $\mathbf{A}$ is invertible and $\lVert
  \mathbf{A}^{-1} \rVert \lVert \mathbf{E} \rVert < 1$, then $\mathbf{A} +
  \mathbf{E}$ is invertible, and
  \[
    \lVert (\mathbf{A} + \mathbf{E})^{-1} \rVert \le \frac{\lVert
      \mathbf{A}^{-1} \rVert}{1 - \lVert \mathbf{A}^{-1} \rVert \lVert
      \mathbf{E} \rVert}.
  \]
\end{lemma}

@@

% TODO: add this lemma to the graph
\begin{lemma} \label{lemma:matrix_inverse}
  TODO: constant bounds on the inverse
\end{lemma}

@@

  Given any covariance matrix $\mathbf{K}$, we can easily establish constant
  upper and lower bounds on $\mathbf{K}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ by the boundedness of $c$ and continuity of the covariance
  function. Similar reasoning combined with the expressions for derivatives of
  covariance matrices in Lemma \ref{lemma:derivatives} gives constant upper and
  lower bounds on the elements of
  \[
    \left. \frac{\mathbf{\partial K}}{\partial \lambda_i} \right|_{\lambda_i =
      c(\mathbf{r}, \mathbf{u})}
  \]
  as well. We can also use Lemma \ref{lemma:matrix_inverse} to show constant
  upper and lower bounds on $\mathbf{K}^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$. This is enough to prove constant upper and lower bounds on
  $\mathbf{S}$, $\bm\Gamma$, and $\mathbf{R}$ (all with $\lambda_i$ replaced
  with $c(\mathbf{r}, \mathbf{u})$), which means that $(\mathbf{r} -
  \mathbf{Su})^\intercal\bm\Gamma^{-1}\mathbf{R}\bm\Gamma^{-1}(\mathbf{r} -
  \mathbf{Su})|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ has upper and lower
  bounds in $\mathbb{R}_2[\mathbf{u}]$.

@@

  TODO: Show that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ is
  bounded.

  Since we already know that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ and $\det(\bm\Gamma)|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$
  are bounded, so is $\adj(\bm\Gamma) =
  \det(\bm\Gamma)\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$. Thus,
  we have constant bounds on
  $|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma))|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$, which means that
  \[
    \left. \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i}
    \right|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  \]
  has the required bounds.

  If $i = 0$, then each element of $\frac{\partial \mathbf{K}}{\partial
    \lambda_0}$ is of the form
  \[
    \exp \left( -\frac{1}{2}(\mathbf{x}_j - \mathbf{x}_k)^\intercal
      \bm\Lambda (\mathbf{x}_j - \mathbf{x}_k) - \mathbbm{1}[j \ne
      k]\sigma^2\tr(\bm\Lambda) \right),
  \]
  i.e., without $\lambda_0$, so
  \[
    \left. \frac{\partial \mathbf{K}}{\partial \lambda_0} \right|_{\lambda_0 =
      c(\mathbf{r}, \mathbf{u})} = \frac{\partial \mathbf{K}}{\partial
      \lambda_0}
  \]
  is already independent of $\mathbf{r}$ and $\mathbf{u}$---there is no need
  for any bounds.

  If $i > 0$, then each element of $\frac{\partial \mathbf{K}}{\partial
    \lambda_i}$ is a constant multiple of $k(\mathbf{x}_j,
  \mathbf{x}_k)$, for some $\mathbf{x}_j$ and $\mathbf{x}_k$. Since
  $k(\mathbf{x}_j, \mathbf{x}_k)$ is a decreasing function of
  $\lambda_i$, and $c(\mathbf{r}, \mathbf{u}) > a$,
  \begin{alignat*}{3}
    k(\mathbf{x}_j, \mathbf{x}_k)|_{\lambda_i = c(\mathbf{r},
      \mathbf{u})} &= \lambda_0 \exp \left( \vphantom{\frac{1}{2}} \right. &&
    -\frac{1}{2} c(\mathbf{r}, \mathbf{u})(x_{j,i} - x_{k,i})^2 \\
    & && - \mathbbm{1}[j \ne k]\sigma^2c(\mathbf{r}, \mathbf{u}) - S \left.
      \vphantom{\frac{1}{2}} \right) \\
    &< \lambda_0 \exp \left( \vphantom{\frac{1}{2}} \right. && -\frac{1}{2}
    a(x_{j,i} - x_{k,i})^2 \\
    & && - \mathbbm{1}[j \ne k]\sigma^2a - S \left. \vphantom{\frac{1}{2}}
    \right),
  \end{alignat*}
  where
  \[
    S = \sum_{n \in \{ 1, \dots, d \} \setminus \{ i \}} \frac{\lambda_n}{2}
    (x_{j,n} - x_{k,n})^2 + \mathbbm{1}[j \ne k]\sigma^2 \lambda_n,
  \]
  which gives an upper bound on each element of
  \[
    \left. \frac{\partial \mathbf{K}}{\partial \lambda_i} \right|_{\lambda_i =
      c(\mathbf{r}, \mathbf{u})}.
  \]
  A similar line of reasoning establishes lower bounds as well.

  % TODO: Lemma 1.1 is wrong about the derivative. Fix (my handwritten notes
  % have the correct idea)
  Combining the bounds with the observation that
  every element of
  $\Kuu^{-1}\mathbf{u}\mathbf{u}^\intercal\Kuu^{-\intercal}$ is in
  $\mathbb{R}_2[\mathbf{u}]$ gives the required result.
\end{proof}

@@

\begin{lemma} \label{lemma:bound3}
  Let $i, j = 1, \dots, m$, and let $\epsilon > 0$ be arbitrary. Furthermore,
  let
  \[
    c : \mathbb{R}^{|\mathcal{S}|} \times \mathbb{R}^m \to (\Sigma_{i,j} - \epsilon,
    \Sigma_{i,j} + \epsilon) \subset \mathbb{R}
  \]
  be a function with a codomain arbitrarily close to $\Sigma_{i,j}$. Then every
  element of
  \[
    \left. \frac{\partial q(\mathbf{u})}{\partial \bm\Sigma} \right|_{\Sigma_{i,j} =
    c(\mathbf{r}, \mathbf{u})}
  \]
  has upper and lower bounds of the form $q(\mathbf{u})d(\mathbf{u})$, where
  $d(\mathbf{u}) \in \mathbb{R}_2[\mathbf{u}]$.
\end{lemma}
\begin{proof}
  Using Lemma \ref{lemma:derivatives},
  \[
    \left. \frac{\partial q(\mathbf{u})}{\partial \bm\Sigma} \right|_{\Sigma_{i,j} =
    c(\mathbf{r}, \mathbf{u})} =
    \frac{1}{2}q(\mathbf{u})(\mathbf{C}(\mathbf{r},
    \mathbf{u})^{-\intercal}\mathbf{UC}(\mathbf{r}, \mathbf{u})^{-\intercal} -
    \mathbf{C}(\mathbf{r}, \mathbf{u})^{-\intercal}),
  \]
  where
  \[
    [\mathbf{C}(\mathbf{r}, \mathbf{u})]_{k,l} =
    \begin{cases}
      c(\mathbf{r}, \mathbf{u}) & \text{if } (k, l) = (i, j), \\
      \Sigma_{k,l} & \text{otherwise.}
    \end{cases}
  \]
  We can also express $\mathbf{C}(\mathbf{r},\mathbf{u})$ as
  $\mathbf{C}(\mathbf{r}, \mathbf{u}) = \bm\Sigma + \mathbf{E}(\mathbf{r},
  \mathbf{u})$, where
  \[
    [\mathbf{E}(\mathbf{r}, \mathbf{u})]_{k,l} =
    \begin{cases}
      c(\mathbf{r}, \mathbf{u}) - \Sigma_{i,j} & \text{if } (k, l) = (i, j), \\
      0 & \text{otherwise.}
    \end{cases}
  \]
  We begin by establishing upper and lower bounds on $\mathbf{C}(\mathbf{r},
  \mathbf{u})^{-1}$. For this, we use the maximum norm $\lVert \cdot
  \rVert_\infty$ on both vectors and matrices. We can apply Lemma
  \ref{prop:condition_number} to $\bm\Sigma$ and $\mathbf{E}(\mathbf{r},
  \mathbf{u})$ since
  \[
    \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty = \max_k \sum_l
    |[\mathbf{E}(\mathbf{r}, \mathbf{u})]_{k,l}| = |c(\mathbf{r}, \mathbf{u}) -
    \Sigma_{i,j}| < \epsilon
  \]
  can be made arbitrarily small so that $\lVert \bm\Sigma^{-1} \rVert_\infty
  \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty < 1$. Then
  $\mathbf{C}(\mathbf{r}, \mathbf{u})$ is invertible, and
  \[
    \lVert \mathbf{C}(\mathbf{r}, \mathbf{u})^{-1} \rVert_\infty \le
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty} <
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  which means that
  \[
    \max_k \sum_l \left| [\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}]_{k,l} \right|
    < \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  i.e., for any row $k$ and column $l$,
  \[
    \left| [\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}]_{k,l} \right| <
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  which bounds all elements of $\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}$ as
  required. Since every element of $\mathbf{U} = (\mathbf{u} - \bm\mu)(\mathbf{u} -
  \bm\mu)^\intercal$ is in $\mathbb{R}_2[\mathbf{u}]$, and the elements of
  $\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}$ are bounded, the desired result
  follows.
\end{proof}

>>>>

\begin{abstract}
  We prove the validity of performing variational inference on the Gaussian
  process-based inverse reinforcement learning model that preserves and
  approximates the full joint probability distribution of rewards across states
  of the Markov decision process.
\end{abstract}

@@

\begin{lemma}[Perturbation Lemma
  \cite{layton2014numerical}] \label{lemma:perturbation}
  Let $\lVert \cdot \rVert$ be any matrix norm, and let $\mathbf{A}$ and
  $\mathbf{E}$ be matrices such that $\mathbf{A}$ is invertible and $\lVert
  \mathbf{A}^{-1} \rVert \lVert \mathbf{E} \rVert < 1$, then $\mathbf{A} +
  \mathbf{E}$ is invertible, and
  \[
    \lVert (\mathbf{A} + \mathbf{E})^{-1} \rVert \le \frac{\lVert
      \mathbf{A}^{-1} \rVert}{1 - \lVert \mathbf{A}^{-1} \rVert \lVert
      \mathbf{E} \rVert}.
  \]
\end{lemma}

@@

@@

  Given any covariance matrix $\mathbf{K}$, we can easily establish constant
  upper and lower bounds on $\mathbf{K}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ by the boundedness of $c$ and continuity of the covariance
  function. Similar reasoning combined with the expressions for derivatives of
  covariance matrices in Lemma \ref{lemma:derivatives} gives constant upper and
  lower bounds on the elements of
  \[
    \left. \frac{\mathbf{\partial K}}{\partial \lambda_i} \right|_{\lambda_i =
      c(\mathbf{r}, \mathbf{u})}
  \]
  as well.

  First, we will show that $\mathbf{K}^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ has constant bounds. If $i = 0$, then $\mathbf{K}|_{\lambda_i
    = c(\mathbf{r}, \mathbf{u})} = c(\mathbf{r}, \mathbf{u})\mathbf{A}$, where
  $\mathbf{A}$ is a constant matrix defined by
  \[
    \mathbf{A} = \frac{1}{\lambda_0}\mathbf{K},
  \]
  and, thus, is invertible.
  Therefore,
  \[
    \mathbf{K}^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} =
    \frac{1}{c(\mathbf{r}, \mathbf{u})}\mathbf{A}^{-1}.
  \]
  Since $\lambda_0$ cannot be zero, we can make $\epsilon$ small enough so that
  either $\lambda_0 - \epsilon > 0$ or $\lambda_0 + \epsilon < 0$, i.e., the
  values of $c(\mathbf{r}, \mathbf{u})$ are either all positive or all negative.
  Then, by continuity of $x \mapsto \frac{1}{x}$, $\mathbf{K}^{-1}|_{\lambda_i =
    c(\mathbf{r}, \mathbf{u})}$ has constant bounds.

  Let
  \[
    S = \sum_{n \in \{ 1, \dots, d \} \setminus \{ i \}} \frac{\lambda_n}{2}
    (x_{j,n} - x_{k,n})^2 + \mathbbm{1}[j \ne k]\sigma^2 \lambda_n
  \]
  and $\delta = c(\mathbf{r}, \mathbf{u}) - \lambda_i$ so that $c(\mathbf{r},
  \mathbf{u}) = \lambda_i + \delta$. If $i > 0$, then
  \begin{align*}
    &k(\mathbf{x}_j, \mathbf{x}_k)|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} = \!\begin{multlined}[t]
      \lambda_0 \exp \left( \vphantom{\frac{1}{2}} \right. -\frac{1}{2} c(\mathbf{r}, \mathbf{u})(x_{j,i} - x_{k,i})^2\\
      - \mathbbm{1}[j \ne k]\sigma^2c(\mathbf{r}, \mathbf{u}) - S \left. \vphantom{\frac{1}{2}} \right)
    \end{multlined} \\
    &= \!\begin{multlined}[t]
      \lambda_0 \exp \left( \vphantom{\frac{1}{2}} \right. -\frac{1}{2} (\lambda_i + \delta)(x_{j,i} - x_{k,i})^2 \\
      - \mathbbm{1}[j \ne k]\sigma^2(\lambda_i + \delta) - S \left. \vphantom{\frac{1}{2}} \right)
    \end{multlined} \\
    &= \!\begin{multlined}[t]
      \lambda_0 \exp \left( \vphantom{\frac{1}{2}} \right. -\frac{1}{2}(\mathbf{x}_j - \mathbf{x}_k)^\intercal \bm\Lambda (\mathbf{x}_j - \mathbf{x}_k) - \mathbbm{1}[j \ne k]\sigma^2\tr(\bm\Lambda) \\
      - \frac{\delta}{2}(x_{j,i} - x_{k,i})^2 - \mathbbm{1}[j \ne k]\sigma^2\delta \left. \vphantom{\frac{1}{2}} \right)
    \end{multlined} \\
    &= k(\mathbf{x}_j, \mathbf{x}_k)\exp \left( \vphantom{\frac{1}{2}} \right. -\frac{\delta}{2}(x_{j,i} - x_{k,i})^2 - \mathbbm{1}[j \ne k]\sigma^2\delta \left. \vphantom{\frac{1}{2}} \right) \\
    &= \!\begin{multlined}[t]
      k(\mathbf{x}_j, \mathbf{x}_k) + k(\mathbf{x}_j, \mathbf{x}_k) \left( \exp
        \left( -\frac{\delta}{2}(x_{j,i} - x_{k,i})^2 \right. \right. \\
      -\mathbbm{1}[j \ne k]\sigma^2\delta \left. \left. \vphantom{\frac{1}{2}} \right) - 1 \right)
    \end{multlined}
  \end{align*}
  Hence, we can express $\mathbf{K}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ as
  $\mathbf{K}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} = \mathbf{K} +
  \mathbf{E}$, where
  \[
    E_{j,k} = k(\mathbf{x}_j, \mathbf{x}_k) \left( \exp \left(
        -\frac{\delta}{2}(x_{j,i} - x_{k,i})^2 \right. \right. -\mathbbm{1}[j
    \ne k]\sigma^2\delta \left. \left. \vphantom{\frac{1}{2}} \right) - 1
    \right).
  \]
  Note that $E_{j,k} \to 0$ as $\delta \to 0$ and $\delta$ can be made
  arbitrarily small via $\epsilon$. Then, since $\mathbf{K}$ is invertible, we
  can make $\delta$ small enough so that $\lVert \mathbf{K}^{-1} \rVert_\infty
  \lVert \mathbf{E} \rVert_\infty < 1$, and Lemma \ref{lemma:perturbation} shows
  the existence of $\mathbf{K}^{-1}_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ and
  gives upper and lower bounds on all of its elements.

  This is enough to prove constant upper and lower bounds on
  $\mathbf{S}$, $\bm\Gamma$, and $\mathbf{R}$ (all with $\lambda_i$ replaced
  with $c(\mathbf{r}, \mathbf{u})$), which means that $(\mathbf{r} -
  \mathbf{Su})^\intercal\bm\Gamma^{-1}\mathbf{R}\bm\Gamma^{-1}(\mathbf{r} -
  \mathbf{Su})|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ has upper and lower
  bounds in $\mathbb{R}_2[\mathbf{u}]$.

@@

  TODO: Show that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ is
  bounded. Might need something similar to the matrix bound lemma, since the
  definition of $\bm\Gamma$ involves addition.

  Since we already know that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ and $\det(\bm\Gamma)|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$
  are bounded, so is $\adj(\bm\Gamma) =
  \det(\bm\Gamma)\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$. Thus,
  we have constant bounds on
  $|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma))|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$, which means that
  \[
    \left. \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i}
    \right|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  \]
  has the required bounds.
\end{proof}

@@

\begin{lemma} \label{lemma:bound3}
  Let $i, j = 1, \dots, m$, and let $\epsilon > 0$ be arbitrary. Furthermore,
  let
  \[
    c : \mathbb{R}^{|\mathcal{S}|} \times \mathbb{R}^m \to (\Sigma_{i,j} - \epsilon,
    \Sigma_{i,j} + \epsilon) \subset \mathbb{R}
  \]
  be a function with a codomain arbitrarily close to $\Sigma_{i,j}$. Then every
  element of
  \[
    \left. \frac{\partial q(\mathbf{u})}{\partial \bm\Sigma} \right|_{\Sigma_{i,j} =
    c(\mathbf{r}, \mathbf{u})}
  \]
  has upper and lower bounds of the form $q(\mathbf{u})d(\mathbf{u})$, where
  $d(\mathbf{u}) \in \mathbb{R}_2[\mathbf{u}]$.
\end{lemma}
\begin{proof}
  Using Lemma \ref{lemma:derivatives},
  \[
    \left. \frac{\partial q(\mathbf{u})}{\partial \bm\Sigma} \right|_{\Sigma_{i,j} =
    c(\mathbf{r}, \mathbf{u})} =
    \frac{1}{2}q(\mathbf{u})(\mathbf{C}(\mathbf{r},
    \mathbf{u})^{-\intercal}\mathbf{UC}(\mathbf{r}, \mathbf{u})^{-\intercal} -
    \mathbf{C}(\mathbf{r}, \mathbf{u})^{-\intercal}),
  \]
  where
  \[
    [\mathbf{C}(\mathbf{r}, \mathbf{u})]_{k,l} =
    \begin{cases}
      c(\mathbf{r}, \mathbf{u}) & \text{if } (k, l) = (i, j), \\
      \Sigma_{k,l} & \text{otherwise.}
    \end{cases}
  \]
  We can also express $\mathbf{C}(\mathbf{r},\mathbf{u})$ as
  $\mathbf{C}(\mathbf{r}, \mathbf{u}) = \bm\Sigma + \mathbf{E}(\mathbf{r},
  \mathbf{u})$, where
  \[
    [\mathbf{E}(\mathbf{r}, \mathbf{u})]_{k,l} =
    \begin{cases}
      c(\mathbf{r}, \mathbf{u}) - \Sigma_{i,j} & \text{if } (k, l) = (i, j), \\
      0 & \text{otherwise.}
    \end{cases}
  \]
  We begin by establishing upper and lower bounds on $\mathbf{C}(\mathbf{r},
  \mathbf{u})^{-1}$. For this, we use the maximum norm $\lVert \cdot
  \rVert_\infty$ on both vectors and matrices. We can apply Lemma
  \ref{lemma:perturbation} to $\bm\Sigma$ and $\mathbf{E}(\mathbf{r},
  \mathbf{u})$ since
  \[
    \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty = \max_k \sum_l
    |[\mathbf{E}(\mathbf{r}, \mathbf{u})]_{k,l}| = |c(\mathbf{r}, \mathbf{u}) -
    \Sigma_{i,j}| < \epsilon
  \]
  can be made arbitrarily small so that $\lVert \bm\Sigma^{-1} \rVert_\infty
  \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty < 1$. Then
  $\mathbf{C}(\mathbf{r}, \mathbf{u})$ is invertible, and
  \[
    \lVert \mathbf{C}(\mathbf{r}, \mathbf{u})^{-1} \rVert_\infty \le
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \lVert \mathbf{E}(\mathbf{r}, \mathbf{u}) \rVert_\infty} <
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  which means that
  \[
    \max_k \sum_l \left| [\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}]_{k,l} \right|
    < \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  i.e., for any row $k$ and column $l$,
  \[
    \left| [\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}]_{k,l} \right| <
    \frac{\lVert \bm\Sigma^{-1} \rVert_\infty}{1 - \lVert \bm\Sigma^{-1}
      \rVert_\infty \epsilon},
  \]
  which bounds all elements of $\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}$ as
  required. Since every element of $\mathbf{U} = (\mathbf{u} - \bm\mu)(\mathbf{u} -
  \bm\mu)^\intercal$ is in $\mathbb{R}_2[\mathbf{u}]$, and the elements of
  $\mathbf{C}(\mathbf{r}, \mathbf{u})^{-1}$ are bounded, the desired result
  follows.
\end{proof}
